{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-13 paper/paper.tex
formulated more precisely

To connect programs and security levels, a \textit{security environment}
(se) is defined, which is used to prevent flows over implicit channels.
A security environment is a function that maps program points to security
levels. A program point $i$ is called high if $se(i) = high$, low if $se(i)
= low$ and always high if all points $j$ reachable (according to $\mapsto$)
from $i$ satisfy $se(j) = i$ and $i$ is high.

>>>>

To connect programs and security levels, a \textit{security environment}
(se) is defined, which is used to prevent flows over implicit channels.
A security environment is a function that maps program points to security
levels. A program point $i$ is called high if $se(i) = high$, low if $se(i)
= low$ and always high if all points $j$ reachable (according to $\mapsto$)
from $i$ satisfy $se(j) = i$ and $i$ is a high program point.

Now we come to the semantics part.
